%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \vspace{-4.0mm}
%---------------------------------------------------------
  \cventry
    {Virologist - Bioinformatician} % Job title
    {US Centers for Disease Control and Prevention - Viral Vaccine Preventable Diseases Branch} % Organization
    {Atlanta, USA} % Location
    {2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Led a laboratory genomics unit, analyzing time-critical outbreak investigation data.}
        \item {Consulted on molecular surveillance of vaccine-preventable childhood diseases, including measles, mumps, rubella, and others.}
        	\item {Led development of multiple whole-genome sequencing assays for measles and mumps clinical specimens.}
	\item {Led genetic studies of measles virus transmission.}
	\item {Led studies contributing to revision of measles virus molecular nomenclature.}
	\item {Consulted extensively on the use of Bayesian phylogenetic methods.}
	 \item {Established partnerships and delivered genomics data to domestic and international stakeholders.}
	 \item {Published findings in peer-reviewed articles.}
      \end{cvitems}
    }
  \vspace{2.0mm}
  
  %---------------------------------------------------------
  \cventry
    {Virologist - Bioinformatician} % Job title
    {US Centers for Disease Control and Prevention - COVID-19 Pandemic Response} % Organization
    {Atlanta, USA} % Location
    {2020 - 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Developed backend applications to scale ETLs of SARS-CoV-2 sequence data from multiple offsite sources. Current daily refresh volume is > 16 million sequences plus metadata.}
        \item {Performed unit and regression testing to ensure quality and error-tolerance of viral sequence processing applications.}
	 \item {Monitored and optimized performance of distributed databases.}
        \item {Consulted on implementation of phylogenetic modeling for molecular studies of SARS-CoV-2 surveillance datasets.}
	\item {Analyzed SARS-CoV-2 sequence repositories with machine learning models (Collaboration: MIT) to predict immunologically significant sequence divergence.}
        \item {Contributed findings to peer-reviewed articles.}
        \item {Languages: Scala, Python, R, SQL}
	\item {Frameworks: Apache Spark, Hadoop, HDFS, YARN, Apache Hive/Impala, Nextstrain}
      \end{cvitems}
    }
  \vspace{2.0mm}
  
  
  
  \end{cventries}
